partial: An R Package for Creating Partial Dependence Plots

### 2016-08-10 manuscript/greenwell.tex
minor updates

Setting up a parallel backend is rather straightforward. To illustrate, the following snippet of sets up the \code{partial} function to run in parallel on Unix-like systems\footnote{This example will not run on Windows.} using the \pkg{doParallel}.
\begin{example}
library(doParallel)  # load parallel backend
registerDoParallel(cores = 4)  # use 4 cores
\end{example}
Now, to run \code{partial} in parallel, all we have to do is invoke the \code{.parallel = TRUE} option and the rest is taken care of by the internal call to \pkg{plyr} the parallel backend we loaded. This is illustrated in following snippet of code which obtains the partial dependence of median home value on $\boldsymbol{z}_s = \left\{\code{rm}, \code{ptratio}, \code{chas}\right\} in parallel. The result is displayed in Figure~\ref{fig:partial_par}.
\begin{example}
partial(boston.rf, pred.var = c("rm", "ptratio", "chas"), grid.resolution = 20, 
        chull = TRUE, .parallel = TRUE, plot = TRUE)
\end{example}

>>>>

Setting up a parallel backend is rather straightforward. To illustrate, the following snippet of sets up the \code{partial} function to run in parallel on Unix-like systems\footnote{This example will not run on Windows.} using the \pkg{doParallel}.
\begin{example}
library(doParallel)  # load parallel backend
registerDoParallel(cores = 4)  # use 4 cores
\end{example}
Now, to run \code{partial} in parallel, all we have to do is invoke the \code{.parallel = TRUE} option and the rest is taken care of by the internal call to \pkg{plyr} the parallel backend we loaded. This is illustrated in following snippet of code which obtains the partial dependence of median home value on $\boldsymbol{z}_s = \{$\code{rm}, \code{ptratio}, \code{chas}$\}$ in parallel. The result is displayed in Figure~\ref{fig:partial_par}.
\begin{example}
partial(boston.rf, pred.var = c("rm", "ptratio", "chas"), grid.resolution = 20,
        chull = TRUE, .parallel = TRUE, plot = TRUE)
\end{example}
